Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-04 paper/main.tex
move stimulus annotation to statistical analysis
table moving madness

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
and compare current results to results that we gained from a dedicated visual
localizer experiment conducted with the same 14 participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show
significantly increased activation restricted to the anterior part of the PPA
that was defined using the visual localizer [as well as in the retrosplenial
and lateral occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort.
%
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different cognitive and perceptual
functions.
%%%%%%%%%%%%%%%%%%%%%% trenne diese Sätze %%%%%%%%%%%%%%5
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways of processing
different kind of visual information:
% dorsal vs ventral pathway
a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
ventral pathway that leads into into the temporal lobe (the ``what pathway'')
\citep{goodale1992separat, mishkin1982contribution}.
%
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus is not anatomically but
functionally defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
%
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% disandvantage of stimuli and block
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approch improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% mirror images
Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
% controlled luminance and size
Images were matched in luminance and size of 400 $\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle.
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

\subsection{Naturalistic stimuli annotation}

\todo[inline]{Ich würde abschnitt 2.8 (statistical analysis) teilen:
    a) die regressors, die dann mit der beschreibung der annotation kombinieren
    b) die eigentliche statistik)}

%
Since we did not design the given naturalistic stimuli for optimal localization
performance of the PPA, we operationalized the perception of landscapes and
landmarks (compared to e.g. faces and objects) by annotating words spoken by the
narrator of the audio-description as well as cuts and depicted locations in the
movie.
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

\todo[inline]{Ich merke das mal hier an: Die Tables stehen an ganz merkwürdigen
Positionen, das passt nicht zum Text und verwirrt ungemein}

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-description's
            narrator: categories, annotation rules, and examples (given in
            English). The category \texttt{++} also contains adverbial of time.}
            \label{tab:descr-nouns-rules} \begin{tabular}{lll} \toprule
                \textbf{category} & \textbf{rule} & \textbf{examples} \\
                \midrule body & trunk of the body; overlaid clothes & back, hip,
                shoulder; jacket, dress, shirt \tabularnewline bodypart & limbs
                and trousers & arm, finger, leg, toe \tabularnewline face & face
                or parts of it & face, ear, nose, mouth \tabularnewline female &
                female person & nurse, mother, woman \tabularnewline females &
                female persons & women \tabularnewline fname & female name &
                Jenny \tabularnewline furniture & movable furniture insides \&
                outsides & bench, bed, table, chair \tabularnewline geo &
                immobile landmarks & building, tree, street, alley, meadow,
                cornfield \tabularnewline geo-room & rooms (insides) or  locales
                (outsides) & living room; wall, door, window, floor, turf
                \tabularnewline head & non-face parts of the head; worn headgear
                & head, hair, ear, neck, helmet \tabularnewline male & male
                person & man, father, soldier \tabularnewline males & male
                persons & boys, opponents \tabularnewline mname & male name &
                Bubba, Kennedy \tabularnewline object & countable entity with
                firm boundaries & telephone, car \tabularnewline objects &
                countable entities & wheels, plants \tabularnewline persons &
                concrete persons of unknown sex & hippies, patients
                \tabularnewline setting\_new & noun cueing an unfamiliar setting
                &  on a ``bridge'', on an ``alley'', on ``campus''
                \tabularnewline setting\_rec & noun cueing a recurring setting &
                at the ``bus stop'' \tabularnewline ++ & cue regarding time & in
                the ``evening'', it's ``daytime'', ``later'' \tabularnewline

\bottomrule \end{tabular} \end{table*}

% table of descriptive nouns counts
\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-descriptions
        narrator: counts for the whole audio-only stimulus and its eight
    segments used during fMRI scanning.} \label{tab:descr-nouns-counts}
    \begin{tabular}{llllllllll} \toprule \textbf{category} & \textbf{all} &
        \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} &
        \textbf{6} & \textbf{7} & \textbf{8} \\ \midrule body & \anBodyAll &
        \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI &
        \anBodyVII & \anBodyVIII \tabularnewline bodypart &  \anBodypartAll &
        \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV &
        \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII
        \tabularnewline face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII &
        \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII
        \tabularnewline female & \anFemaleAll & \anFemaleI & \anFemaleII &
        \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII &
        \anFemaleVIII \tabularnewline females & \anFemalesAll & \anFemalesI &
        \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI
        & \anFemalesVII & \anFemalesVIII \tabularnewline fname & \anFnameAll &
        \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV &
        \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline furniture &
        \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII &
        \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII &
        \anFurnitureVIII \tabularnewline geo & \anGeoAll & \anGeoI & \anGeoII &
        \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII
        \tabularnewline geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII &
        \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI &
        \anGeoroomVII & \anGeoroomVIII \tabularnewline head & \anHeadAll &
        \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI &
        \anHeadVII & \anHeadVIII \tabularnewline male & \anMaleAll & \anMaleI &
        \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII &
        \anMaleVIII \tabularnewline males & \anMalesAll & \anMalesI & \anMalesII
        & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII &
        \anMalesVIII \tabularnewline mname & \anMnameAll & \anMnameI &
        \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI &
        \anMnameVII & \anMnameVIII \tabularnewline object & \anObjectAll &
        \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV &
        \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline objects &
        \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII &
        \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII &
        \anObjectsVIII \tabularnewline persons & \anPersonsAll & \anPersonsI &
        \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI
        & \anPersonsVII & \anPersonsVIII \tabularnewline

setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII &
\anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI &
\anSettingnewVII & \anSettingnewVIII \tabularnewline

setting\_rec & \anSettingrecAll & \anSettingrecI & \anSettingrecII &
\anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI &
\anSettingrecVII & \anSettingrecVIII \tabularnewline ++ & \anAll & \anI & \anII
& \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline \bottomrule
\end{tabular} \end{table*}

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.

% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
volumes for segment 1–8).

@@

@@

\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
der beschreibung der annotation kombinieren, und die eigentliche statistik)}

Similarly to the reviewed studies that employed simplified stimuli, we conducted
a standard two-level general linear model (GLM) analysis to create
subject-specific results ($Z$-maps) across the 8 segments for every subject. A
subsequent, third-level analysis averaged contrast estimates over subjects.

\todo[inline]{better speak of conditions than categories?}

\todo[inline]{Ich würde vorschlagen, dass Du Dich auf die Regressoren / Events
konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die aber
dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist ein
setting "familiar"?}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
$t$-contrasts and compare current results to results that we gained from a
dedicated visual localizer experiment conducted with same participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show significantly
increased activation restricted to the anterior part of the PPA that was defined
using the visual localizer [as well as in the retrosplenial and lateral
occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort.
%
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different cognitive and perceptual
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways of processing
different kind of visual information:
% dorsal vs ventral pathway
a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
ventral pathway that leads into into the temporal lobe (the ``what pathway'')
\citep{goodale1992separat, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus is not anatomically but
functionally defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
% conceptualized stimuli and blockl: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approch improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% mirror images
Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
volumes for segment 1–8).

@@

% intro
Similarly to the reviewed studies that employed simplified stimuli, we conducted
a standard two-level general linear model (GLM) analysis to create
subject-specific results ($Z$-maps) across the 8 segments for every subject. A
subsequent, third-level analysis averaged contrast estimates over subjects.

@@

\todo[inline]{SE: focus on the events that are relevant to the analysis to
reduce complexity and explain these better}

\todo[inline]{Simon suggested to put paragraphs regarding annotation here,
    followed by a subsection ``Regressors''. Additionally imo, it makes sense to
    build one subsection ``Stimulus annotations \& regressors'' to have a
    structure of ``AO (anno \& regressors); AV (anno \& regressors'' instead of
AO \& AV (annotation), AO \& AV (regressors)``.}

% intro
Since we did not design the naturalistic stimuli for detection power, we
operationalized the perception of landscapes and landmarks (compared to e.g.
faces and objects) by annotating words spoken by the narrator of the
audio-description as well as cuts and depicted locations in the movie.
% stimuli not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

% table for descriptive nouns: categories, rules, examples counts
% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Descriptive nouns spoken by the audio-description's narrator that
        served as a basis to build the regressors
(see Table \ref{tab:ao-events}):
    categories, annotation rules, and examples (given in English).
    % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}
